Synthesizing Symmetric Lenses

### 2018-07-07 papers/SymmetricLenses/main.tex
nits

To overcome this second difficulty, we turned to information theory to try to
find a way to characterize the likely and unlikely lenses. Intuitively, a
``likely'' lens is one that propagates a lot of information from source to
target and also from target back to source. Conversely, given the source, the
target is ``unlikely'' to require very much additional information in order to
reconstruct it, under the assumption that users typically want to synchronize
formats with a large amount of shared information. In order to implement this
intuition, we turn to \emph{stochastic regular expressions} (SREs). Stochastic
regular expressions define a set of strings, as do ordinary regular expressions,
but they also provide the expected distribution of strings within that set. Such
distributions allow us to compute the amount of information gained when
presented an element of the set. For example, the language of the SRE
$\lstinline{"a"} |_{0.5}
\lstinline{"b"}$ contains two elements (the strings \lstinline{"a"} and \lstinline{"b"}).
The probability 0.5 annotating the union indicates that both elements are
equally likely to appear. Consequently, if we observe an element of that
language (either \lstinline{"a"} or
\lstinline{"b"}), we will gain one bit of information. Said another way, one bit, together with
the SRE, suffices to recover the string in question. Interestingly, if the
probability annotation were anything but 0.5, the expected information content
(or entropy) would actually be less than 1 (given a stream of such choices, on
average we could encode the the contents of stream in fewer bits than the the
number of choices present). On the other hand, consider the language of the SRE
\lstinline{c}. It contains just one element (the string $c$). If we observe that
our algorithm generates $\lstinline{"c"}$, we gain zero bits of information ---
the string was already determined. Using this foundation, a lens $\Lens \OfType
\Regex \Leftrightarrow \RegexAlt$ is ``likely,''
in a technical sense, if given a string $s$ in the source $S$, very little information
is needed to determine which synchronized string $t$ is present in the target
$T$.

@@

\subsection{Simple Symmetric Lenses}
A simple symmetric lens between formats described by types $\Regex$
and $\RegexAlt$ 
is defined by four functions\bcp{I think a picture would be helpful.  I can probably
  make one pretty easily by tweaking the one from the original symmetric paper.}
\afm{That would be awesome.}

>>>>

To overcome this second difficulty, we turned to information theory to try to
find a way to characterize the likely and unlikely lenses. Intuitively, a
``likely'' lens is one that propagates a lot of information from source to
target and also from target back to source. Conversely, given the source, the
target is ``unlikely'' to require very much additional information in order to
reconstruct it, under the assumption that users typically want to synchronize
formats with a large amount of shared information. In order to implement this
intuition, we turn to \emph{stochastic regular expressions} (SREs). Stochastic
regular expressions define a set of strings, as do ordinary regular expressions,
but they also provide the expected distribution of strings within that set. Such
distributions allow us to compute the amount of information gained when
presented an element of the set. For example, the language of the SRE
$\lstinline{"a"} |_{0.5}
\lstinline{"b"}$ contains two elements (the strings \lstinline{"a"} and \lstinline{"b"}).
The probability 0.5 annotating the union indicates that both elements are
equally likely to appear. Consequently, if we observe an element of that
language (either \lstinline{"a"} or
\lstinline{"b"}), we will gain one bit of information. Said another way, one bit, together with
the SRE, suffices to recover the string in question. Interestingly, if the
probability annotation were anything but 0.5, the expected information content
(or entropy) would actually be less than 1 (given a stream of such choices, on
average we could encode the the contents of stream in fewer bits than the the
number of choices present). On the other hand, consider the language of the SRE
\lstinline{c}. It contains just one element (the string $c$). If we observe that
our algorithm generates $\lstinline{"c"}$, we gain zero bits of information ---
the string was already determined. Using this foundation, a lens $\Lens$ that
synchronizes data between $\Regex$ and $\RegexAlt$ is ``likely,''
in a technical sense, if given a string $s$ in the source $S$, very little information
is needed to determine which synchronized string $t$ is present in the target
$T$.

@@

\subsection{Simple Symmetric Lenses}
A simple symmetric lens between formats described by types $\BRegex$
and $\RegexAlt$ 
is defined by four functions\bcp{I think a picture would be helpful.  I can probably
  make one pretty easily by tweaking the one from the original symmetric paper.}
\afm{That would be awesome.}
